\cvsection{Personal Project}
\begin{cventries}
  \cventry
    {back end development, Java}
    {AI Music Generation and Recommendation Website}
    {}
    {Feb. 2021 - May. 2021}
    {
      \begin{cvitems}
        \item {Support user to collection music, fork a user and generate a piece of music based on their preferences. Personalized music recommendation is also available.}
        \item {Docker was used to deploy this project.}
        \item {Technology stack: SpringBoot, MySQL, Redis, MongoDB, Kafka}
      \end{cvitems}
    }
  \cventry
    {front end development, Remax}
    {WeChat Mini Program Development}
    {}
    {Dec. 2020 - Mar. 2021}
    {
      \begin{cvitems}
        \item {Online card game named Who Is Undercover.  Support multi-user room creation, role assignments, game review and other functions.}
      \end{cvitems}
    }

    \cventry
    {Android}
    {Android Maze Game Development based on AR.}
    {}
    {Sep. 2019 - Dec. 2019}
    {
      \begin{cvitems}
        \item {Obtain the tracking picture in the user's album, render the 3D maze and player model in real time according to the picture.
        }
        \item{Interaction between the player model and the 3D maze model.}
        \item{Realize basic functions such as game countdown, user scoring, score ranking.}
      \end{cvitems}
    }
    
  \cventry
    {Tensorflow}
    {Application of dynamic graphs in the classification of malicious programs}
    {}
    {Mar. 2021 - Jun. 2021}
    {
      \begin{cvitems}
        \item {Use dynamic interaction to model the Sample-API network. GRU structure was used to update the representation of sample and API respectively.}
        \item {Read data from MongoDB, which contains samples and the API call sequence.}
        \item {Group samples according to the correlation between APIs. Train the model by using dynamic batch processing algorithms.}
      \end{cvitems}
    }
\end{cventries}
